Principles for Open Data Curation: A Case Study with the New York City 311 Service Request Data

### 2024-09-28 manuscript/manuscript.tex
comments on presentations

@@

@@

\jy{This is caused by reading the number in as double
  precision. Single precision would be good.}

@@

\textbf{borough \& taxi\_company\_borough:} Despite their names, these 
fields are almost entirely different, with only a 0.05\% match. The 
\texttt{taxi\_company\_borough} field is used exclusively by the TLC, 
indicating a need for consultation with TLC to understand the differing 
uses.

@@

>>>>

\jy{If the 10-year data was only used for Figure~\ref{fig:10-yr}, we
  could remove this figure and just describe it in text. This would
  avoid the confusion of which dataset was used in the analyses in the
  sequel.}

\jy{If we keep the 10-year data, we might as well make some dynamic
  visualization over time. For example, Figure 2/3 could have multiple
  panels such that we can see several 2-year decompositions over
  time.}

@@

\jy{Currently we have 9 figures and 3 tables, which are too many for
  an article. Some journal (e.g., Biometrics) requires no more than 6
  tables/figures combines. We need to more selective in presenting
  figures/tables, perhaps no more than 8 combined?
}

@@

\jy{This is caused by reading the number in as double
  precision. Single precision would be good. The raw csv file only
  have 7 digits after the decimal point, e.g.,
  $(40.769737, -73.91244)$.
  }

@@

\textbf{borough \& taxi\_company\_borough:} Despite their names, these 
fields are almost entirely different, with only a 0.05\% match. The 
\texttt{taxi\_company\_borough} field is used exclusively by the TLC, 
indicating a need for consultation with TLC to understand the differing 
uses.
\jy{The taxi\_company\_borough may mean the borough of the location of
  the taxi company, which can be irrelevant to the borough where the
  incident was reported.. Such information could be useful only when
  studying TLC related SRs. It'd be better to use a second table to
  store such TLC dependent information.}

@@

\jy{In my Chance article, we found an agency
  `DEPARTMENT OF CONSUMER AND WORKER PROTECTION', which occurred 361
  times in May 2023. It was the only one that does not look like an
  acronym. Did this occur in the two-year data?
  I wonder if this has been fixed lately.}

\jy{A related question is whether the data quality has improved over
  the years}
